--
title: "Mini Challenge 1 - The Visual Detective"
description: |
    In the roughly twenty years that Tethys-based GAStech has been operating a natural gas production site in the island country of Kronos, it has produced remarkable profits and developed strong relationships with the government of Kronos. However, GAStech has not been as successful in demonstrating environmental stewardship.
   
    In January, 2014, the leaders of GAStech are celebrating their new-found fortune as a result of the initial public offering of their very successful company. In the midst of this celebration, several employees of GAStech go missing. An organization known as the Protectors of Kronos (POK) is suspected in the disappearances.
    
    It is January 21, 2014, and as an expert in visual analytics, you have been tasked with helping people understand the complex relationships among people and organizations that may have contributed to these events.
    
    *Background*
    This scenario and all the people, places, groups, technologies, contained therein are fictitious. Any resemblance to real people, places, groups, or technologies is purely coincidental.

author:
  - name: Amrita Mishra
    url: https://amritamishradatablog.netlify.app/
date: 07-18-2021
output:
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
packages = c('tidytext', 'widyr',
              'wordcloud', 'DT',
              'textplot','lubridate',
              'hms','tidyverse',
              'tidygraph','ggraph',
              'igraph')

for(p in packages){
  if(!require(p, character.only = T)){
    install.packages(p)
  }
  library(p, character.only = T)
}
```

```{r}
news20 <- "data/MC1/"
```

